% =====================================
% HARITHA N – One Page MNC-Ready Resume
% =====================================

\documentclass[10pt,a4paper]{article}

% ---------------- Packages ----------------
\usepackage[left=1.1cm,right=1.1cm,top=1.1cm,bottom=1.1cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{parskip}

\pagestyle{empty}

% ---------------- Fonts & Section Style ----------------
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\setstretch{0.93}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{4pt}{4pt}

\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=0.15in}

% ---------------- Custom Commands ----------------
\newcommand{\resumeItem}[1]{\item #1}
\newcommand{\resumeSubheading}[4]{
  \item
    \textbf{#1} \hfill {\small #2} \\
    {\small #3} \\
    {\small #4}
}

\begin{document}

%====================
% Header
%====================
\begin{center}
    {\LARGE \textbf{HARITHA N}}\\[-2pt]
    Chennai, Tamil Nadu, India \textbullet{} +91 9043080876 \\
    \href{mailto:haritha11479@gmail.com}{haritha11479@gmail.com} \textbullet{}
    \href{https://www.linkedin.com/in/haritha-n-ba5abb37b}{LinkedIn} \textbullet{}
    \href{https://github.com/haritha-n}{GitHub}
\end{center}

%====================
% Career Objective
%====================
\section*{Career Objective}
Aspiring software professional seeking a role to leverage Python, web development, and cloud skills to build scalable, user-friendly applications and contribute to innovative projects in a dynamic MNC environment.

%====================
% Education
%====================
\section*{Education}
\textbf{MCA}, Dr. M.G.R. Educational and Research Institute \hfill 2023 -- 2025, \textit{CGPA: 8.76} \\
\textbf{BCA}, Dr. M.G.R. Educational and Research Institute \hfill 2020 -- 2023, \textit{CGPA: 8.85} \\
\textbf{12th}, Pioneer Matric Hr. Sec. School \hfill 2019 -- 2020, \textit{60.67\%} \\
\textbf{10th}, Pioneer Matric Hr. Sec. School \hfill 2017 -- 2018, \textit{61.60\%}

%====================
% Technical Skills
%====================
\section*{Technical Skills}
\begin{itemize}
    \resumeItem{\textbf{Programming:} Python, SQL -- Automation, backend development, data analysis}
    \resumeItem{\textbf{Web:} HTML, CSS, JavaScript -- Interactive front-end development}
    \resumeItem{\textbf{Tools \& Platforms:} AWS (Basic), Git, VS Code}
    \resumeItem{\textbf{Other Skills:} Data Analytics, Big Data Pipelines, Cloud Deployment}
\end{itemize}
%====================
% GitHub & Portfolio
%====================
\section*{GitHub \& Portfolio}
\begin{itemize}
    \resumeItem{\textbf{GitHub Profile:} \href{https://github.com/haritha-n}{github.com/haritha-n}}
    \resumeItem{\textbf{Resume Source Code (LaTeX):} \href{https://github.com/haritha-n/resume}{github.com/haritha-n/resume}}
\end{itemize}


%====================
% Internship / Experience
%====================
\section*{Internship Experience}
\begin{itemize}
\resumeSubheading
{Tech Power Solutions – Web Development Intern}{Feb 2025 -- Present}{Chennai, India}{
\begin{itemize}
    \item Developed front-end and back-end components using React.js, Vue.js, Node.js, MongoDB
    \item Implemented responsive design and database integration
    \item Collaborated on debugging, testing, and deploying small-scale applications
\end{itemize}}
\end{itemize}

%====================
% Projects
%====================
\section*{Projects}
\begin{itemize}
\resumeSubheading
{Cloud Data Integrity Auditing}{Feb 2025 -- May 2025}{}{ABAC-based cloud security with Hyperledger blockchain; deployed on AWS using Python for tamper-proof verification.
\href{https://github.com/haritha-n/cloud-data-integrity}{GitHub Repository}
}

\resumeSubheading
{Message Encoder/Decoder in Python}{Mar 2023 -- Apr 2023}{}{GUI messaging app with Tkinter and Base64 encoding; implemented face recognition authentication for secure communication}
\end{itemize}

%====================
% Certifications & Training
%====================
\section*{Certifications \& Training}
\begin{itemize}
    \resumeItem{NPTEL Database Management Systems (Swayam) -- SQL, relational databases, transaction management}
    \resumeItem{Python Internship – Tech Power Solutions -- Automated workflows using Python scripts}
    \resumeItem{Web Development Internship – Tech Power Solutions -- Built responsive front-end interfaces}
    \resumeItem{Data Analytics with Databricks (Online) -- Hands-on big data analytics, Python/SQL integration}
    \resumeItem{Interview Skill Development Workshop}
    \resumeItem{Unlocking Your Potential for Success Workshop}
\end{itemize}

%====================
% Personal Strengths
%====================
\section*{Personal Strengths}
\begin{itemize}
    \resumeItem{Creativity, Innovation, Problem-Solving}
    \resumeItem{Decision Making, Prioritization}
    \resumeItem{Time Management, Adaptability}
    \resumeItem{Team Collaboration, Confidence}
\end{itemize}

%====================
% Publications
%====================
\section*{Publications}
\begin{itemize}
    \resumeItem{\textbf{“Attribute Based Cloud Data Integrity Auditing for Secure Outsourced Storage”} — Published in \textit{International Research Journal of Modernization in Engineering Technology and Science (IRJMETS)}, Volume 07, Issue 05, May 2025. \textbf{Paper ID: IRJMETS70500231869}}
\end{itemize}

%====================
% Declaration
%====================
\section*{Declaration}
I hereby declare that all information provided above is true and correct to the best of my knowledge.

\end{document}
